The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2019-11-12 paper.tex
Removed old document headings.
More edits to paper from previous meeting with Jerry.

%\documentclass[english, backref,breaklinks,colorlinks,citecolor=blue, usenatbib]{mnras}
%\usepackage{amsbsy}
%\usepackage{amsmath}
%\usepackage{amstext}
%\usepackage[T1]{fontenc}
%\usepackage[latin9]{inputenc}
%%\usepackage[nobottomtitles]{titlesec}
%\usepackage{array}
%\usepackage{rotating}
%\usepackage{units}
%\usepackage{textcomp}
%\usepackage{graphicx}
%\usepackage{url}
%\usepackage{babel}
%\usepackage{float}
%\usepackage{savesym}
%\savesymbol{tablenum}
%\usepackage{siunitx}
%\restoresymbol{SIX}{tablenum}
%%\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
%\usepackage{hyperref}
%\usepackage{hypcap}

%\makeatletter

%\newcommand{\msun}{\mbox{$\,{\rm M}_\odot$}}

%\sloppy

@@

\subsubsection{Gravitational wave recoils}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in Kulier(+15), which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius. At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned. [STILL NEED TO DESCRIBE KICK AFTER MERGER].

@@

\subsection{Black Hole Luminosity}
The x-ray temperature versus sigma relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
\begin{equation}
    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}.
\end{equation}
Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
\begin{equation}
    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}.
\end{equation}
The core radius of the gas model, ${r_c}$ is:
\begin{equation}
    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
\end{equation}
Local gas density ${\rho}$ is obtained from the isothermal beta model [ADD REFERENCE]:
\begin{equation} \label{beta_model}
    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
\end{equation}

@@

\section{Conclusions}\label{sec:conclusions}
We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.  We found that 42$\%$ of the orbiting black holes merged with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.  With an x-ray luminosity range of $10^{25}-10^{43}$ $erg\ s^{-1}$.

>>>>

@@

\subsubsection{Gravitational wave recoils}
The code \textsc{AR-Chain} includes post-Newtonian terms up to order 2.5. The SMBHs can therefore merge via gravitational wave emission. We include gravitational wave recoils following the prescription outlined in Kulier(+15), which is based on the fitting formula by \citet{2012PhRvD..85h4015L}.  We assume that a merger will be inevitable when the separation between two SMBHs becomes smaller than 1.0x the Schwarzschild radius. At the moment of the merger, we also assume that the spin vectors of the two SBHs are randomly aligned.

A result of the anisotropic emission of gravitational waves is that the merged binary often experiences a linear kick in the opposite direction of the emission of the GW due to conservation of linear momentum. This kick can result in velocities of the merged binary from approximately $200-5000\ km s^{-1}$ (see \citet{2007PhRvL..98w1101G}, \citet{2007PhRvL..98i1101G}, \citet{2007PhRvL..98w1102C}, \citet{2011PhRvL.107w1102L}).  In our simulations, the binaries never stray more than a few tens of parsecs from the nucleus of the host galaxies.

@@

\subsection{Black Hole Luminosity}
The x-ray temperature versus sigma relation from Table 2 of  \citet{2018ApJ...857...32B} was fitted according to:
\begin{equation}
    T_x = 10^{2.50*log(\sigma) - 6.06} \text{  kev}.
\end{equation}
Central gas density, ${\rho}_0$ was also fitted from Table 3 of \citet{2018ApJ...857...32B} according to:
\begin{equation}
    \rho_0 = 10^{0.6*log(\sigma) - 25} \text{  g cm}^{-3}.
\end{equation}
The core radius of the gas model, ${r_c}$ is:
\begin{equation}
    r_c = 10^{2.1*log(\sigma) - 5.3} \text{  kpc}.
\end{equation}
Local gas density ${\rho}$ is obtained from the isothermal beta model (\citet{1962AJ.....67..471K}, \citet{1976A&A....49..137C}, \citet{1978A&A....70..677C}):
\begin{equation} \label{beta_model}
    \rho = \frac{\rho_0}{(1+r^2/r_c^2)^{1.5}} \text{  g cm}^{-3}.
\end{equation}

@@

\section{Conclusions}\label{sec:conclusions}
We performed N-body simulations on 11 galaxies ranging in mass between $10^{12}$ M$_{\sun}$ < M < $10^{13}$ M$_{\sun}$, from 4 $\gid$ z $\gid$ 0.  A total of 86 orbiting black holes were followed in our simulations, resulting in 42$\%$ mergers with their host galaxy, while another 43$\%$ remained in orbit at $z=0$.  Those remaining orbiting black holes had x-ray luminosities in the range of $10^{25}-10^{43}$ $erg\ s^{-1}$.  The median luminosity of $10^{32} erg\ s^{-1}$ would be undetectable with present instruments, although the top $5\%$ most luminous from this set could be detectable.
